Figures compiler

### 2017-12-06 analyses/figures-compiler.Rmd
Multiple plots updated

>>>>

## Load all the data
data_list_max <- lapply(slugs, function(slug) read.csv(paste0("../outputs/peaks.max.", slug, ".csv"), stringsAsFactors = FALSE))
data_list_min <- lapply(slugs, function(slug) read.csv(paste0("../outputs/peaks.min.", slug, ".csv"), stringsAsFactors = FALSE))

## Load the relative time
relative_times <- lapply(slugs, function(slug) read.nexus(file = paste0("../data/processed/tree.", slug, ".tre")))
relative_times <- lapply(relative_times, function(tree) max(tree.age(tree)$age))
relative_times[[4]] <- 484.4

## Set up the colours (to be changed)
colours <- palette()[1:7]

## Plot all maximum ages
multi.plot.max.min(data_list_max, what = c("age"), cols = colours, lty = c(1,2), pch = 19, adj = 0.1, relative.time = relative_times, legend = TRUE, names.data = unlist(slugs))

## Plot all maximum disparity
multi.plot.max.min(data_list_max, what = c("disparity"), cols = colours, lty = c(1,2), pch = 19, adj = 0.1, relative.time = relative_times, names.data = unlist(slugs))

## Plot all minimum ages
multi.plot.max.min(data_list_max, what = c("age"), cols = colours, lty = c(1,2), pch = 19, adj = 0.1, relative.time = relative_times, names.data = unlist(slugs))

## Plot all minimum disparity
multi.plot.max.min(data_list_max, what = c("disparity"), cols = colours, lty = c(1,2), pch = 19, adj = 0.1, relative.time = relative_times, names.data = unlist(slugs))

```
